---
title: "Desafio_Quinto_Andar"
output: pdf_document
date: '2022-06-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eval=F}
library(randomForest)
library(gbm)
library(tidyverse)
library(forecast )
library(ggcorrplot)
library(lares)
library(gridExtra)
library(lubridate)
library(caret)

```


## Set directory 
```{r  }
setwd("~/R_K/tera")
df_raw <- read_csv('base.csv')

df_raw <- df_raw %>% 
  filter(CondicaoVenda == 'Normal')
df_raw
```

## All missing values 
```{r}
sum(is.na(df_raw))
```
## Info 
```{r}
glimpse(df_raw)

```



## Sum NA for each column 
```{r}
sapply(df_raw, function(x) sum(is.na(x)))
```

## Transforming variables as date
```{r}
df <- df_raw

df %>% 
  select(contains(match ='Ano'))
   
df$AnoReforma <- parse_date_time(x = df$AnoReforma, orders = '%Y')
df$AnoGaragem <- parse_date_time(x = df$AnoGaragem, orders = '%Y')
df$AnoVenda <- parse_date_time(x = df$AnoVenda, orders = '%Y')
```

## Selecing only features with less than 500 missing values 
```{r}
df$Id <- NULL

temp <-  lapply(df, function(x) sum(is.na(x)))
temp <- as.data.frame(temp[temp > 500] )
df <- df %>% 
  select(-names(temp))

sapply(df, function(x) sum(is.na(x)))
```

## Plot in loop 

```{r}
df_cat <- df[,!sapply(df, is.numeric)]
df_cat$PrecoVenda <-  df$PrecoVenda
## organizando 
df_cat <-  df_cat %>% 
  select(PrecoVenda, names(df_cat))

df_cat <- df_cat %>% 
  select(-AnoVenda, -AnoGaragem, -AnoReforma)

```

# Saving 
```{r}
plot_list <- list()
for (i in 1:length(df_cat)){
  plot_list[[i]] <- ggplot(df_cat, aes_string( x =names(df_cat[i]), y =names(df_cat[1]))) +
    geom_boxplot()
  
}
```
 

```{r}
v1 <- plot_list[c(2:10)]
do.call(grid.arrange,v1)
```

```{r}
v2 <- plot_list[-1]
v2
```

```{r}
df_num <- df[,sapply(df, function(x) is.numeric(x))]
df_num <- df_num %>% 
  select(PrecoVenda, names(df_num))
df_num
```


# Saving 
```{r}
plot_list <- list()
for (i in 1:length(df_num)){
  plot_list[[i]] <- ggplot(df_num, aes_string( x =names(df_num[i]), y =names(df_num[1]))) +
    geom_point()
  
}
```

```{r}
v2 <- plot_list[-1]
v2
```

```{r}
plot_list <- list()
for (i in 1:length(df_num)){
  plot_list[[i]] <- ggplot(df_num, aes_string( x =names(df_num[i]))) +
    geom_histogram()
  
}
plot_list
```

## Function to tranform char into factor  
```{r}
col_2factor <- function(data){
  datacat <- data[,!sapply(data, is.numeric)]
  datacat <- datacat[,!sapply(datacat, lubridate::is.POSIXct)]
  datacat <- datacat[,!sapply(datacat, lubridate::is.Date)]
  

  datacat <- lapply(datacat, function(x) as.factor(x))
  
  data_temp <- data %>% 
    dplyr::select(-names(datacat))
  
  datan <- dplyr::as_tibble(cbind(data_temp,datacat))
  datan <- dplyr::select(datan,names(data))
  return(datan)
}

```




## Transformando variáveis categóricas em factor
```{r}
df <- col_2factor(df)
str(df) 
```



## Ordinal Encoding 
```{r}


old <- c("Po", "Fa", "TA", "Gd", "Ex"  ) 
new   <- c(1, 2, 3, 4, 5 ) 


df$CondicaoGaragem = as.numeric(plyr::mapvalues(df$CondicaoGaragem, from =old, to = new ))
df[['CondicaoGaragem']][is.na(df[['CondicaoGaragem']])] <- 0

df$QualidadeGaragem = as.numeric(plyr::mapvalues(df$QualidadeGaragem, from =old, to = new ))
df[['QualidadeGaragem']][is.na(df[['QualidadeGaragem']])] <- 0

df$CondicaoExterna = as.numeric(plyr::mapvalues(df$CondicaoExterna, from =old, to = new ))

sapply(df, function(x) sum(is.na(x)))


```

```{r}

old <- c( "Fa", "TA", "Gd", "Ex"  ) 
new   <- c(1, 2, 3, 4  ) 


df$AlturaPorao = as.numeric(plyr::mapvalues(df$AlturaPorao, from =old, to = new ))
df[['AlturaPorao']][is.na(df[['AlturaPorao']])] <- 0

df$QualidadeCozinha = as.numeric(plyr::mapvalues(df$QualidadeCozinha, from =old, to = new ))
df$QualidadeCobertura = as.numeric(plyr::mapvalues(df$QualidadeCobertura, from =old, to = new ))
```

```{r}

old <- c("Po", "Fa", "TA", "Gd" ) 
new   <- c(1, 2, 3, 4 ) 



df$CondicaoPorao = as.numeric(plyr::mapvalues(df$CondicaoPorao, from =old, to = new ))
df[['CondicaoPorao']][is.na(df[['CondicaoPorao']])] <- 0

```


######################################
```{r}

old <- c("Po", "Fa", "TA", "Gd", "Ex"  ) 
new   <- c(1, 2, 3, 4, 5 ) 



df$QualidadeAquecimento = as.numeric(plyr::mapvalues(df$Aquecimento, from =old, to = new ))
table(df$QualidadeAquecimento)

```
##############

## Othes olds and news 


```{r}

old <- c('Gd', 'Av',' Mn', 'No')
new   <- c(1, 2, 3, 4 ) 
df$ParedePorao = as.numeric(plyr::mapvalues(df$ParedePorao, from =old, to = new ))
df[['ParedePorao']][is.na(df[['ParedePorao']])] <- 0

table(train$ParedePorao)
```


```{r}
old <- c('GLQ', "ALQ", "BLQ", "Rec", "LwQ", "Unf")
new   <- c(1, 2, 3, 4,5,6 ) 
df$TipoAcabPorao1 = as.numeric(plyr::mapvalues(df$TipoAcabPorao1, from =old, to = new ))
df[['TipoAcabPorao1']][is.na(df[['TipoAcabPorao1']])] <- 0

df$TipoAcabPorao2 = as.numeric(plyr::mapvalues(df$TipoAcabPorao2, from =old, to = new ))
df[['TipoAcabPorao2']][is.na(df[['TipoAcabPorao2']])] <- 0
```


```{r}

old <- c('2Types', 'Attchd', 'Basment', 'BuiltIn', 'CarPort', 'Detchd')
new   <- c(1, 2, 3, 4,5,6 ) 
df$LocalGaragem = as.numeric(plyr::mapvalues(df$LocalGaragem, from =old, to = new ))
df[['LocalGaragem']][is.na(df[['LocalGaragem']])] <- 0

```


```{r}
old <- c('Fin', 'RFn', 'Unf')
new   <- c(1, 2, 3) 
df$AcabamentoGaragem = as.numeric(plyr::mapvalues(df$AcabamentoGaragem, from =old, to = new ))
df[['AcabamentoGaragem']][is.na(df[['AcabamentoGaragem']])] <- 0

```


```{r}

old <- c('GLQ', 'ALQ', 'BLQ', 'Rec', 'LwQ','Unf' )
new   <- c(1, 2, 3,4,5,6) 
df$TipoAcabPorao1 = as.numeric(plyr::mapvalues(df$TipoAcabPorao1, from =old, to = new ))
df[['TipoAcabPorao1']][is.na(df[['TipoAcabPorao1']])] <- 0

df$TipoAcabPorao2 = as.numeric(plyr::mapvalues(df$TipoAcabPorao2, from =old, to = new ))
df[['TipoAcabPorao2']][is.na(df[['TipoAcabPorao2']])] <- 0

table(df$TipoAcabPorao1)

```

```{r}

index <- createDataPartition(df$PrecoVenda, p =0.7, list = F )
train <-  df[index,]
test <-  df[-index,]

index <- createDataPartition(test$PrecoVenda, p =0.5, list = F )
validation <-  test[index,]

test <-  test[-index,]

```

## Replace missing values to mean 
```{r}
train <- train %>% 
         mutate_if(is.numeric, ~replace_na(.,mean(., na.rm = TRUE)))

validation <- validation %>% 
         mutate_if(is.numeric, ~replace_na(.,mean(., na.rm = TRUE)))

test <- test %>% 
         mutate_if(is.numeric, ~replace_na(.,mean(., na.rm = TRUE)))
```



## Function to replace NA to mode for categorical features 

```{r}


nacat__2mode <- function(data)
  {
  getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
  }
  ## get cat 
  datacat <- data[,!sapply(data, is.numeric)]
  datacat <- datacat[,!sapply(datacat, lubridate::is.POSIXct)]
  ## get vars with na
  temp <- lapply(datacat, function(x) sum(is.na(x)) > 0)
  temp <- as.data.frame(temp[temp=='TRUE'] )
  
  datacat_na <- datacat[colnames(temp)]
  
  ##
  for(i in 1:length(datacat_na)){
    x_dropna <- datacat_na[complete.cases(datacat_na[,i]),i]
    mode <- getmode(x_dropna)
    mode[1,]
    column <- datacat_na[,i]
    column[which(is.na(column)),] <- mode[1,]
    datacat_na[,i] <- column
  }
  data_temp <- data %>% 
    dplyr::select(-names(datacat_na))
  datan <- dplyr::as_tibble(cbind(data_temp,datacat_na))
  datan <- dplyr::select(datan,names(data))
  return(datan)
}
```


## Replacing NA values to mode 
```{r}

train <- nacat__2mode(train)



sapply(validation, function(x) sum(is.na(x)))

```




```{r}
train <- train %>% 
         mutate_if(is.POSIXct, ~replace_na(.,mean(., na.rm = TRUE)))

validation <- validation %>% 
         mutate_if(is.POSIXct, ~replace_na(.,mean(., na.rm = TRUE)))

test <- test %>% 
         mutate_if(is.POSIXct, ~replace_na(.,mean(., na.rm = TRUE)))
```


```{r}
sum(is.na(train))
```
```{r}
sum(is.na(validation))
```
```{r}
sum(is.na(test))
```
## Other way 
```{r}
encode_ordinal <- function(x, order = unique(x)) {
  x <- as.numeric(factor(x, levels = order, exclude = NULL))
  x
}
```

```{r}

train[['FormaProp']] <- encode_ordinal(train[['FormaProp']])
train[['EntradaPavimentada']] <- encode_ordinal(train[['EntradaPavimentada']])
train[['EstiloHabitacao']] <- encode_ordinal(train[['EstiloHabitacao']])

```

```{r}
validation[['FormaProp']] <- encode_ordinal(validation[['FormaProp']])
validation[['EntradaPavimentada']] <- encode_ordinal(validation[['EntradaPavimentada']])
validation[['EstiloHabitacao']] <- encode_ordinal(validation[['EstiloHabitacao']])
```

```{r}
test[['FormaProp']] <- encode_ordinal(test[['FormaProp']])
test[['EntradaPavimentada']] <- encode_ordinal(test[['EntradaPavimentada']])
test[['EstiloHabitacao']] <- encode_ordinal(test[['EstiloHabitacao']])
```

# dummy
```{r}
train[['Rua']] <- encode_ordinal(train[['Rua']])
train[['ArCentral']] <- encode_ordinal(train[['ArCentral']])

```

```{r}
validation[['Rua']] <- encode_ordinal(validation[['Rua']])
validation[['ArCentral']] <- encode_ordinal(validation[['ArCentral']])
```

```{r}
test[['Rua']] <- encode_ordinal(test[['Rua']])
test[['ArCentral']] <- encode_ordinal(test[['ArCentral']])
```

```{r}
train$TipoVenda <- NULL 
train$Outros <- NULL
train$CondicaoVenda <- NULL

```

```{r}
validation$TipoVenda <- NULL 
validation$Outros <- NULL
validation$CondicaoVenda <- NULL

```

```{r}
test$TipoVenda <- NULL 
test$Outros <- NULL
test$CondicaoVenda <- NULL

```

```{r}
train$log_PrecoVenda <- log(train$PrecoVenda)
validation$log_preco_venda <- log(validation$PrecoVenda)
test$log_preco_venda <- log(test$PrecoVenda)

yvalidation <- validation$PrecoVenda
ytest <- test$PrecoVenda

train$PrecoVenda <-  NULL
validation$PrecoVenda <- NULL
test$PrecoVenda <- NULL


``` 
## One hot encoding function
```{r}

one_hot_encoding = function(df, columns="season"){
  # create a copy of the original data.frame for not modifying the original
  df = cbind(df)
  # convert the columns to vector in case it is a string
  columns = c(columns)
  # for each variable perform the One hot encoding
  for (column in columns){
    unique_values = sort(unique(df[column])[,column])
    non_reference_values  = unique_values[c(-1)] # the first element is going 
    # to be the reference by default
    for (value in non_reference_values){
      # the new dummy column name
      new_col_name = paste0(column,'.',value)
      # create new dummy column for each value of the non_reference_values
      df[new_col_name] <- with(df, ifelse(df[,column] == value, 1, 0))
    }
    # delete the one hot encoded column
    df[column] = NULL
    
  }
  return(df)
}
```



## One hot encoding and cleaning names 
```{r}
train <- janitor::clean_names(one_hot_encoding(train, columns = c( 'ClasseZona', 'PlanoProp','Servicos',
                                       'ConfigLote', 'InclinacaoLote', 'Bairro', 'Estrada1',
                                       'Estrada2', 'TipoHabitacao', 'TipoTelhado', 
                                        'Exterior1', 'Exterior2','TipoAlvenaria',
                                       'TipoFundacao', 'Aquecimento','InstalacaoEletrica',
                                       'Funcionalidade','MaterialTelhado' )))

validation <- janitor::clean_names(one_hot_encoding(validation, columns = c( 'ClasseZona', 'PlanoProp','Servicos',
                                       'ConfigLote', 'InclinacaoLote', 'Bairro', 'Estrada1',
                                       'Estrada2', 'TipoHabitacao', 'TipoTelhado', 
                                        'Exterior1', 'Exterior2','TipoAlvenaria',
                                       'TipoFundacao', 'Aquecimento','InstalacaoEletrica',
                                       'Funcionalidade','MaterialTelhado' )))

test <- janitor::clean_names(one_hot_encoding(test, columns = c( 'ClasseZona', 'PlanoProp','Servicos',
                                       'ConfigLote', 'InclinacaoLote', 'Bairro', 'Estrada1',
                                       'Estrada2', 'TipoHabitacao', 'TipoTelhado', 
                                        'Exterior1', 'Exterior2','TipoAlvenaria',
                                       'TipoFundacao', 'Aquecimento','InstalacaoEletrica',
                                       'Funcionalidade','MaterialTelhado' )))
```

```{r}
model_rf <- randomForest(log_preco_venda ~.,data = train, importance = T)
model_rf

```




```{r}
imp <- importance(model_rf)
imp 
```
## Select the top 50 
```{r}

imp = as.data.frame(imp)
imp = imp %>% 
  arrange(desc(imp$`%IncMSE`)) 

imp = imp[c(1:40),]
imp = row.names(imp)
imp

```

```{r}
train2 <-  train[,imp]
train2$log_preco_venda <- train$log_preco_venda
train = train2 
train
```




The best hyperparameters for  random forest.  
```{r}
random_f_model  <- randomForest(log_preco_venda ~.,data = train, importance = T, ntree = 100)


```
## validation avaliation 
```{r}
pred = predict(random_f_model, validation)
pred = exp(pred)
acc = accuracy(pred, yvalidation)
acc
```



## Test avaliation 
```{r}
pred = predict(random_f_model, test)
pred = exp(pred)
acc = accuracy(pred, ytest)
acc
```




## LM model EDA


```{r}
df$PrecoVenda <- NULL
df_num <- train %>% 
  select(where(is.numeric))

corr_var(df, log_preco_venda, top = 15 )

```



## Linear Regression

```{r}
df$log_preco_venda <- log(df$PrecoVenda)


lm_model  <- lm(log_preco_venda ~ AreaPorao+QualidadeCozinha +Lareira+
               Qualidade+AreaConstruida + AnoConstrucao, data= df)

summary(lm_model)
```
## multicollinearity test

```{r}
car::vif(lm_model)
```


```{r}
sum(car::vif(lm_model))
```
## Residual Normality Test 
```{r}
shapiro.test(lm_model$residuals)
```
## homoscedasticity test
```{r}
plot(lm_model$residuals)
```
## Boosting 
```{r}
train2 <- train[, !sapply(train, function(x) is.POSIXct(x))]
```


```{r}
boost_model <- gbm(log_preco_venda ~., data = train2, distribution = "gaussian", n.trees = 500)
summary(boost_model)
```
## Validation accuracy 
```{r}
pred_boost <- predict(boost_model, newdata = validation)
pred_boost <- exp(pred_boost)
acc <- accuracy(pred_boost, yvalidation)
acc
```
## test accuracy 

```{r}
pred_boost <- predict(boost_model, newdata = test)
pred_boost <- exp(pred_boost)
acc <- accuracy(pred_boost, ytest)
acc
```
```





